Making multiple-locus association mapping on a genome-wide scale routine

### 2016-11-16 AM+draft.tex
Revising results - about to start In Figure 1

To asses the computational performance of AMplus against the above discussed software, we conducted a large simulation study. 
In this study, we were interested in how study size impacts performance. We generated data under five different scenarios. 
These are a study of size 150 individuals and 5000 snp (150 X 5K), 350 individuals and 400000 snp (350 X 400K),  1500 individuals and 
50000 snp (1500 x 50K), 2000 individuals and 500000 snp (2000 x 500K), 4000 individuals and 
1500000 snp (4000 x 1.5M), and 10000 individuals and 1500000 snp (10000 x 1.5M).  These scenarios reflect some of the differences in 
study size of GWAS being performed in plants, animals, and humans.

Under each scenario, we generated 100 replicates of data. A replicate consisted of snp and trait data. 
The snp data comes from the publically available 1000 genomes project (phase 3). The quantitative trait data were generated by randomly selecting a set of snp loci, assigning allelic effects to the selected snp, and aggregating these effects for each individual along with random error. The number of snp selected for a replicate is random, having been drawn from a Poisson distribution with mean 30. The quantitative trait was generated to have a heritability of 50\%.

Analyses were performed on a high end desktop computer with dual 8-core Xeon processors, three Kepler Tesla GPUs, and 128 Giggabytes of RAM. 
All implementations except, Gemma, made use of distributed computing for their linear algebra operations through multithreaded blas and lapac libraries.

>>>>

To asses the computational performance of AMplus, we conducted a large simulation study. 
We were interested in  the impact of study size on  performance so we generated data under five different scenarios. 
These are a GWAS of size 150 individuals and 5000 snp (150 X 5K), 350 individuals and 400000 snp (350 X 400K),  1500 individuals and 
50000 snp (1500 x 50K), 2000 individuals and 500000 snp (2000 x 500K), 4000 individuals and 
1500000 snp (4000 x 1.5M), and 10000 individuals and 1500000 snp (10000 x 1.5M).  
We chose these scenarios to reflect some of the different sized GWAS being performed in animals, plants, and humans. 
For each scenario, we generated 100 replicates of data. A single replicate consists of snp genotype data and quantitative trait data. 
We obtained the snp data from the publicly available 1000 genome project (phase 3). The quantitative trait data we generated from the 
snp data by selecting a set of snp loci, assigning allelic effects to these snp, and aggregating these effects for each individual along with 
random error. The number of snp selected per replicate follows a Poisson distribution with mean 30.
 The quantitative trait was generated to have a heritability of 50\%.
Analyses were performed on a high end desktop computer. It had dual 8-core Xeon processors, three Kepler Tesla GPUs, and 128 Giggabytes of RAM. All implementations except, GEMMA, made use of distributed computing, either explicitly or implicitly through multi-threaded BLAS and LAPACK libraries.
